%
% File: chap01.tex
% Author: Liam O'Shea
% Description: Introduction chapter where the boxing goes.
%
\let\textcircled=\pgftextcircled
\chapter{Introduction}
\label{chap:intro}

\initial{C}omputer aided coaching has revolutionised training approaches and been a key driver in improving sports performance at the highest level.\cite{ISP}Professional athletes can now use advanced augmented coaching to accurately and reliably collect measurements that can then used as indicators of performance.\cite{aug0} This gives the coaching teams unique insight which they use to tailor training programs to give the athlete a goal to focus on and improve.
Huge injections of research funding in preparation for the London Olympics such as The Elite Sport Performance Research in Training (ESPRIT) Programme, meant that UK Sport was allocated \textsterling $2,000,000$  while the Engineering and Physical Sciences Research Council were allocated \textsterling $6,119,249$.\cite{EPSRC} \cite{aug5} 
This money was spent on enhancing elite performance training with technology \cite{aug3} \cite{aug4} which allowed British Olympians to take advantage of these training methods and return with a medal record making it the most successful team since $1908$.\cite{olymp1} These hi-tech training methods were used by Team GB Boxing \cite{aug2} and have started to become incorporated in the USA Boxing team.\cite{aug1}

However despite the recent success, sports technology is still in its infancy, with the majority of devices being expensive, specialist and proprietary\cite{aug7}. There is an array of consumer devices such as the Fitbit, Nike+ Fuelband, Garmin Vivofit and Jawbone that function as general activity trackers but there is currently nothing that offers specialist training or coaching advice. The purpose of ZeroToHero was to use an already widespread, low cost consumer device to bring specialist boxing coaching to everyone. The low-cost is especially crucial since most boxing clubs struggle with funding, rely on volunteers and traditionally have members that are the young and least wealthy in society. ZeroToHero explores the ability of the Kinect to act as a electronic boxing trainer, offering advice on punch and stance performance.
%=======
\section{Goals}
\label{sec:sec01}

\begin{enumerate}
  \item To recognise that a punch is being thrown
  \item To successfully classify this punch 
  \item To classify between a good and bad punch
\end{enumerate}

\subsection{Scope}
\label{subsec:subsec01}
For the course of this project the `orthodox' stance will be used, meaning only those who are right handed will benefit from this system initially. However once the concept is proven it would be trivial to adjust this for `southpaws' since the principles and foundations are exactly the same. The only difference will be that the right hand side of the body will be the more dominant and will be physically closer to the Kinect instead of the left hand side.