%
% File: chap01.tex
% Author: Liam O'Shea
% Description: Introduction chapter where the boxing goes.
%
\let\textcircled=\pgftextcircled
\chapter{Evaluation & Discussion}
\label{chap:intro}

Conclusions, and future work

\initial{B}egins a chapter. Example: When the beloved cellist (Christopher Walken - outstanding) of a world-renowned string quartet receives a life-changing diagnosis, the group's future suddenly hangs in the balance: suppressed emotions, competing egos and uncontrollable passions threaten to derail years of friendship and collaboration. Featuring a brilliant ensemble cast (including Philip Seymour Hoffman, Catherine Keener and Mark Ivanir as the three other quartet members), it is a fascinating look into the world of working musicians, and an elegant homage to chamber music and the cultural world of New York. The music, of course, is ravishing (the score is the work of regular David Lynch collaborator Angelo Badalamenti): A Late Quartet hits all the right notes.


\section{Difficulties}
I found this project to be an excellent way to combine my interest in boxing with my Computer Science background. It was however a difficult project and I ran into a few problems.

\paragraph{Normalisation}


%=======
\section{Section}
\label{sec:sec01}

Begins a section.

\subsection{Subsection}
\label{subsec:subsec01}

Begins a subsection.
Avg Classification score random forest: 78.931% 
Avg Classification score decision tree: 90.882% 

Notes:
Missing why some classifiers perform better than others?
Why does random forest do a worst job than a descicion tree?
More maths?

%=========================================================